Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-03-30 paper/ms.tex
rewriting

We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ between
$9.2$ up to $13.4$, corresponding to the halo mass range of 
the simulation at $z=3$.  
We restrict the selection to models that give a minimal number density 
$N_{\rm{halos}}>N_{\rm LAE}/3$.   
This means that it is possible to have $N_{\rm{halos}} < N_{\rm LAE}$
and hence $\focc\equiv N_{\rm{LAE}}/N_{\rm{halos}}>1$.   
This only reflects the uncertainty in the number 
density of LAEs due to cosmic variance.

@@

\subsection{Median Halo Mass Within Models}

We now compute the median mass, $\log M_{50}$, of the LAE hosting halos for each model
$\mathcal{M}$; $\log M_{50}$ allows a direct comparison between our
results and previous results in the literature
\citep[e.g.][]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16} that used
a more simplified approach.

In   Fig. \ref{fig:mmed} we
show the 50 ($\log M_{50}$, black dots), the 84 ($\log M_{84}$,blue
diamonds) and 95 ($\log M_{95}$, red squares) percentiles of the LAE
halo mass as a function of \lmmin\ for each of the models that we run
in our MCMC simulation.  The points are color coded according to their
\dlm\ associated value. We can see that the median mass ($M_{50}$) and
$M_{84}$ are not very sensitive to  $\lmmax=\lmmin +\dlm$ specially
when $\dlm\gtrsim1.0$dex. We particularly found that
$\lmmin\lesssim\log M_{50}\lesssim\lmmin+0.2\rm{dex}$ and that
$\lmmin+0.1\rm{dex}\lesssim\log M_{50}\lesssim\lmmin+0.5\rm{dex}$
regardless of the value of \dlm. The latter is a consequence of the
very steepen distribution of the dark matter mass function  and is at
the same time the reason for the almost perfect one to one relation
between \mmin\ and \focc. However, it can also be seen in
Fig. \ref{fig:mmed} that $\log M_{84}$ is very sensitive to \lmmax
($\lmmin+0.2\rm{dex}\lesssim\log
M_{50}\lesssim\lmmin+1.5\rm{dex}$). Thereby, any differences in the
clustering strength of models sharing the same \mmin but different
\mmax should be mainly driven by the  $\sim16\%$ most massive  halos
of each model $\mathcal{M}$.

>>>>

We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ between
$9.2$ up to $13.4$, corresponding to the halo mass range of 
the simulation at $z=3$.  
We restrict the selection to models that give a minimal number density 
$N_{\rm{halos}}>N_{\rm LAE}/3$.   
This means that it is possible to have $N_{\rm{halos}} < N_{\rm LAE}$
and hence $\focc\equiv N_{\rm{LAE}}/N_{\rm{halos}}>1$.   
We include the $1/3$ factor to account for the uncertainty in the number 
density of LAEs due to cosmic variance, expecting it to be on the
same order as the dark matter halo cosmic variance shown in
Fig. \ref{fig:cosmicv0}.

@@

\subsection{Median Halo Mass and Halo Mass Width within Models}

We now compute the median mass, $\log M_{50}$, and the $1\sigma$ halo mass
width, $\Delta M_{1\sigma} \equiv \log M_{84} - \log M_{16}$, of the LAE hosting halos for each model
$\mathcal{M}$ (here $M_{p}$ represents the $p$ percentile of the mass distribution);
$\log M_{50}$ and $M_{1\sigma}$ allow a direct comparison between our
results and previous results in the literature
\citep[e.g.][]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16} that used
a more simplified approach.

In Fig. \ref{fig:mmed} we show the $\log M_{50}$-$\Delta M_{1\sigma}$
plane for the models selected in the $1\sigma$ posterior region for
\mmin. The color encodes the $\mmin$ value.

The points are color coded according to their
\dlm\ associated value. We can see that the median mass ($M_{50}$) and
$M_{84}$ are not very sensitive to  $\lmmax=\lmmin +\dlm$ specially
when $\dlm\gtrsim1.0$dex. We particularly found that
$\lmmin\lesssim\log M_{50}\lesssim\lmmin+0.2\rm{dex}$ and that
$\lmmin+0.1\rm{dex}\lesssim\log M_{50}\lesssim\lmmin+0.5\rm{dex}$
regardless of the value of \dlm. The latter is a consequence of the
very steepen distribution of the dark matter mass function  and is at
the same time the reason for the almost perfect one to one relation
between \mmin\ and \focc. However, it can also be seen in
Fig. \ref{fig:mmed} that $\log M_{84}$ is very sensitive to \lmmax
($\lmmin+0.2\rm{dex}\lesssim\log
M_{50}\lesssim\lmmin+1.5\rm{dex}$). Thereby, any differences in the
clustering strength of models sharing the same \mmin but different
\mmax should be mainly driven by the  $\sim16\%$ most massive  halos
of each model $\mathcal{M}$.
